Sparse Function-space Representation \\ of Neural Networks

### 2023-08-04 paper/main.tex
small fix in CL experiments

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI. We also introduce an ablation study where we replace our $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to having an L2 regularization between current and old function outputs.
In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points for S-MNIST.

>>>>

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: Online-EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI. We also introduce an ablation study where we replace our $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to having an L2 regularization between current and old function outputs.
In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points for S-MNIST.
